simulation & inference of transients

### 2019-07-15 notebook/may-outbreak.Rmd
larger learning space

```{r}
possible_a <- seq(.26, .33, by = 0.01)

@@

```{r}
mu <- possible_a[true_i - 2]
prior <- dnorm(possible_a, mu, 0.01)
prior <- prior / sum(prior)
```

@@

```{r}
sim <- mdp_learning(transition, reward, discount, 
                    x0 = x0, 
                    Tmax = Tmax, 
                    true_transition = transition[[true_i]],
                    model_prior = prior,
                    type = "policy iteration")
```

@@

```{r}
mu <- possible_a[true_i + 2]
prior <- dnorm(possible_a, mu, 0.01)
prior <- prior / sum(prior)
```

@@

```{r}
sim <- mdp_learning(transition, reward, discount, 
                    x0 = x0, 
                    Tmax = Tmax, 
                    true_transition = transition[[true_i]],
                    model_prior = prior,
                    type = "policy iteration")
```

>>>>

```{r}
possible_a <- seq(.25, .34, by = 0.005)

@@

```{r}
mu <- possible_a[true_i - 8]
prior <- dnorm(possible_a, mu, 0.01)
prior <- prior / sum(prior)
```

@@

```{r}
sim <- mdp_learning(transition, reward, discount, 
                    x0 = x0, 
                    Tmax = Tmax, 
                    true_transition = transition[[true_i]],
                    model_prior = prior,
                    type = "value iteration", 
                    epsilon = 1e-2)
```

@@

```{r}
mu <- possible_a[true_i + 8]
prior <- dnorm(possible_a, mu, 0.01)
prior <- prior / sum(prior)
```

@@

```{r}
sim <- mdp_learning(transition, reward, discount, 
                    x0 = x0, 
                    Tmax = Tmax, 
                    true_transition = transition[[true_i]],
                    model_prior = prior,
                    type = "value iteration",
                    epsilon = 1e-2)
```

```{r}
sim$df %>% mutate(state = states[state], action = actions[action]) %>% 
  ggplot(aes(time, state)) + geom_point()+geom_path() + 
  geom_line(aes(time, action), col="blue")
```
